Machine Learning Model for Agricultural Data Applications

### 2021-04-12 chapters/implementation.tex
Extract_of_ETL

This work is focused on estimation of Gross-Production Value (GPV), indicative of GDP, based on wheat crop information of Hungary. Finding the right data was been quite tedious. The data set was collected  from the United Nations Food and Agriculture Organization (UN-FAO) databases. The goal was to estimate GPV as the function of agri-land (Hectares) used for wheat, wheat quantity (Tons) produced and the crop yield (Hg/Ha – Hectogram/Hectares). All four variables could not be found in a single data-set. They were found in four different data-sets, but from the single source. The pertinent data-sets contained too much extra and irrelevant information. Using Pandas, the data-sets were cleaned, and desired variables were collected into one data-set a tabular frame using the year as the index. A glimpse of the data-frame is shown below:

@@

\subsection{Data Cleaning}

@@

Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Data Set.

@@

\section{Implementing Machine Learning Work Flow}

\subsection{Assembling the Data Set}
\section{How I implemented the Neural Networks}
\section{Recurring Neural Network}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.35\textwidth]{fig/rnn.png}
	\caption{Recurrent Neural Network (RNN)}
	\label{fig:rnn}
\end{figure}
A representative RNN is shown in Figure ~\ref{fig:rnn} showing the hidden layer. The updating of the weight is accomplished as the function of current inputs and previous outputs. Usually, the weights are updated on the basis of output gradients. The weights are only updated, if the underlying gradients are non-zero. As the learning goes on, gradients begin to vanish. At sometimes the gradients are zero, but they should not be. In deep learning literature, this phenomenon is termed as gradient-vanishing problem - GVP \cite{haykin2009neural}. To avoid GVP, two variants of RNNs have been proposed. LSTM (Long-Short Term Memory) recurrent neural network and GRU (Gated-Recurrent Unit).

>>>>

To extract data, apart from the source, which has already been mentioned as the FAO, the format has to be considered. Data can be provided in various formats like a csv file, xml file, json object just to mention a few. the extracted Data for my work was in a csv file format.

This work is focused on estimation of Gross-Production Value (GPV), indicative of GDP, based on wheat crop information of Hungary. The goal was to estimate GPV as the function of agri-land (Hectares) used for wheat, wheat quantity (Tons) produced and the crop yield (Hg/Ha Hectogram/Hectares). All four variables could not be found in a single data-set. They were found in four different data-sets, but from the single source.

Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Wheat Area-harvested Data Set.

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/Quantity_Head.png}
	\caption{Raw Data Quantity.}
	\label{fig:Quantity_Head}
\end{figure}

Figure \ref{fig:Quantity_Head} shows the top 5 rows of the Quantity Data Set.

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/GPV_Head.png}
	\caption{Raw Data Gross Production Value.}
	\label{fig:GPV_Head}
\end{figure}

Figure \ref{fig:GPV_Head} shows the top 5 rows of the Gross Production Value Data Set.

@@

\subsection{Data Transformation}

This is the data-validation step. The guiding principle is:

\textquote{The garbage in, garbage out (GIGO) is the concept that flawed, or nonsense input data produces nonsense output or garbage}

The pertinent data-sets contained too much extra and irrelevant information. Using Pandas, the data-sets were cleaned, and desired variables were collected into one data-set a tabular frame using the year as the index. A glimpse of the data-frame is shown below:

@@

@@

\section{Data Loading}
\section{The Neural Networks}
\section{Recurring Neural Network}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.35\textwidth]{fig/rnn.png}
	\caption{Recurrent Neural Network (RNN)}
	\label{fig:rnn}
\end{figure}
A representative RNN is shown in Figure ~\ref{fig:rnn} showing the hidden layer. The updating of the weight is accomplished as the function of current inputs and previous outputs. Usually, the weights are updated on the basis of output gradients. The weights are only updated, if the underlying gradients are non-zero. As the learning goes on, gradients begin to vanish. At sometimes the gradients are zero, but they should not be. In deep learning literature, this phenomenon is termed as gradient-vanishing problem - GVP \cite{haykin2009neural}. To avoid GVP, two variants of RNNs have been proposed. LSTM (Long-Short Term Memory) recurrent neural network and GRU (Gated-Recurrent Unit).
